%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
   {Software Developer Intern} % Job title
    {Trendyol.com, Istanbul} % Organization
    {Istanbul, Turkey} % Location
    {July. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on the back-end side of Marketplace project.}  
        \item {Implementing new features and microservices to Supplier and Admin Portal.}
        \item {Developing REST API using Java Spring Boot Framework.}
        \item {Using agile software, pair programming and test driven development methods.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Koc University, Arcelik Research Center for Creative Industries} % Organization
    {Istanbul, Turkey} % Location
    {Oct. 2016 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       	\item {Worked on an Internet of Things(IoT) project which was proposed by me and funded by Arcelik.}
       	\item {Built and deployed overall system and developed simple Android application with Raspberry pi, image, temperature and weight sensors.  }
       	\item {Used machine learning algorithm for food recognition and several AWS stack(Including Rekognition, S3, Dynamodb, Lambda, Cognito).} 
         \item {Worked on a research about applications of wearable technologies and prototyping the project with Arduino and 3D Printing.  }
      \end{cvitems}
    }
\begin{comment}
%---------------------------------------------------------
  \cventry
    {Work \& Study} % Job title
    {Koc University, Computer Information Technology Department} % Organization
    {Istanbul, Turkey} % Location
    {OCt. 2015 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Applied and tested Google Cloud technologies across the campus.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{comment}
\end{cventries}
