%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Change Maker - Vice Presedent of Koc University Makerspace Lab} % Affiliation/role
    {Global Learning and Leadership Program} % Organization/group
    {Koc Universtiy} % Location
    {Sept. 2016-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Cofounder of the team which achieved make an impact and open a Makerspace in campus.}
        \item {Managing the team members and coordinating them.}
        \item {Arranging seminars and workshops about creative skills, popular topics and social innovation. }
        \item {Giving technical advices to students who have projects and helping them to prototype their ideas.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Reviewer and Participant} % Affiliation/role
    {Algorithm Competition Programme} % Organization/group
    {Inzva, Istanbul} % Location
    {Oct. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participating in the 30-week Algorithm Competition Programme, divided into Fall and Spring semesters, which includes lectures, contests, problem-solvings and a variety of practises every saturday.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Section Leader } % Affiliation/role
    {Standford – Koc CS Bridge Program} % Organization/group
    {Koc Universtiy} % Location
    {Summer 2017-Summer 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Was section leader of a Java teaching program directed by Nick McKeown who has taught computer science at Stanford for 20 years.}
        \item {Was responsible for preparing and grading assignments, conducting problem solving sections, helping students during lab-hours and giving feedbacks to daily assignments.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Association for Computing Machinery Society} % Organization/group
    {Koc Universtiy} % Location
    {Oct. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Responsible for organizing IoT and robotics related workshops, conferences for new members. }
        \item {Developing tech-projects to attend national and international competitions. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Global Volunteer in Egypt } % Affiliation/role
    {AIESEC} % Organization/group
    {Cairo, Egypt} % Location
    {Summer 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Was a member of an international team of 30 people which was responsible from building a school from throw-out materials in a poor island in Egypt. }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
